---
title: "vonMisesModel_1stStepFitData"
output: html_document
---

```{r loadData}
rm(list=ls())
library(pracma)
library(ggplot2)
library(ggthemes)
#library(nlme)
library(plyr)
library(reshape2)
#library(circular)
#library(CircStats)
#library(stats4)
#library(bbmle)
library(proto)
library(nls2)
library(scales)
#library(minpack.lm)
library(gridExtra)
options(device='quartz') # open new plot window
#setwd("~/Dropbox/withArman/FFTvoxel") # working directory
setwd("/Users/tancy/Desktop/FFTprocess/FFTvoxel") # working directory

rawData <- read.csv('/Users/tancy/Desktop/FFTprocess/SigCh_HighRes_8s2.csv') # load all data

unique(rawData$Subj)
# select single subject data and drop unuseful columns
BRtestData <- droplevels(subset(rawData, Subj=="S06", select = -c(orient45, ampval, phval, covval)))

# create a new dataframe for model fitting of each block
Block_fun <- function(x, y) rep(1:x, each = length(unique(y)))

# get number of blocks in each voxel
VoxBlock <- droplevels(ddply(BRtestData, .(Voxel), summarise,
                                nblock = length(SingleVolume)/length(unique(SingleVolume))))

# generate a data with sequence of blocks and sequence of HRF                
NewBRtestData <- droplevels(ddply(BRtestData, .(Voxel), transform,
                               Block = Block_fun(VoxBlock$nblock[1], SingleVolume),
                               seqHRF = seq(1, length(HRF))))


head(NewBRtestData)


saveCSV1 <- 'fitVM_Stp1_S06_8s_sm_HR_kap10pi.csv'
saveCSV2 <- 'fitVM_Stp1_S06_8s_sm_HR_kap10pi_RData.csv'
savRDdata <- 'fitVM_Stp1_S06_8s_sm_HR_kap10pi.RData'

```


*** temporal smoothing TS ***
Moving averages for linear filters
$$
Tt = 1/2a+1\Sigma{a, i=-a} Xt+i
$$
the filtered value of a time series at a given period \tau is represeted by the average of the values
{x\tau-a,...,x\tau,...,x\tau+a}. The coefficients of the filtering are {1/(2a+1), ..., 1/(2a+1)}.
```{r smoothTS}
VolSMdata <- droplevels(ddply(NewBRtestData, .(Voxel), function(datTS){
  #browser()
  smTS <- ts(datTS$HRF, start=1, frequency=length(unique(NewBRtestData$Block)))
  linfitTS <- filter(smTS, filter=rep(1/3,3), method="conv", side=2) # apply moving average 
  linfitTS[is.na(linfitTS)] <- mean(linfitTS, na.rm=TRUE)
  seqHRF <- datTS$seqHRF
  linBind <- cbind(seqHRF, linfitTS)  
  }))

# merge with original data
NewBRtestData$seqHRF <- as.numeric(NewBRtestData$seqHRF)
NewBRtestData_SM <- merge(NewBRtestData, VolSMdata, by=c("Voxel","seqHRF"))
NewBRtestData_SM <- arrange(NewBRtestData_SM,Voxel,seqHRF)
head(NewBRtestData_SM)

# randSM <- droplevels(subset(NewBRtestData_SM, r2>.06))
# randSM2 <- (subset(randSM, Voxel==c(13)))
# #plot raw HFR and smooth HRF
# dev.new()
# ggplot(randSM2) + 
#   geom_point(aes(x=seqHRF, y=HRF, colour="rawHRF"), size = 0.5) +
#   geom_line(aes(x=seqHRF, y=HRF, colour="rawHRF")) +
#   #geom_point(aes(x=seqHRF, y=linfitTS, colour="smoothHRF"), size= 0.1) +
#   geom_line(aes(x=seqHRF, y=linfitTS, colour="smoothHRF"), size= 0.5) +
#   facet_wrap(~Voxel, scales='free') + 
#   scale_colour_manual("",values=c("smoothHRF"="red","rawHRF"="blue"))

```


# get zScore 
```{r zScore}
Zdata <- droplevels(ddply(NewBRtestData_SM, .(Voxel), transform,
                          zSigCh = scale(HRF),
                          zSigSM = scale(linfitTS)))
head(Zdata)
#hist(Zdata$zSigCh) # plot histogram

avgZSigCh <- droplevels(ddply(Zdata, .(Voxel, SingleVolume), summarise,
                              nlength = length(unique(Block)),
                              avgSigCh = mean(zSigCh),
                              avgSigSM = mean(zSigSM),
                              steSigSM = sd(zSigSM)/sqrt(nlength)))

rm(list=c("BRtestData", "VolSMdata", "NewBRtestData", "NewBRtestData_SM"))
   
```


*** summary of 1st_fitVM result***
## get paramters and statistics to dataframe
## 1) We fit fixed 13 VM (-pi/2 to pi/2) of each block(trial) 
## 2) Then, we got maxAmp of each VM in each block
## 3) We used 13 maxAmp to get "fitted BOLD resp" of each block
## 4) Finally, we average "fitted BOLD resp" across all blocks
## 5) We can get 13 orient(-90, -75, -60...0,..,90) BOLD resp of each voxel
```{r fitVMresult}


#*** dat to fit VM ***
#```{r ModelFit}
datToFit <- Zdata
head(datToFit)
length(unique(datToFit$Voxel))
vonMisesFit <- vonMises_1stFitData(datToFit)


vonFitCurve <- data.frame()
nVol <- length(unique(datToFit$SingleVolume)) # create seq of nVol
for (iVox in 1:length(vonMisesFit)){
  vonFitBlock <- data.frame()
  for (iBlock in 1:length(unique(datToFit$Block))){
     IdvCurve <-  data.frame(do.call(rbind, lapply(1:length(vonMisesFit[[iVox]][[2]][[iBlock]][[2]]), function(iVM) 
      cbind(vonMisesFit[[iVox]]$Voxel, vonMisesFit[[iVox]][[2]][[iBlock]]$Block,c(1:nVol), rep(iVM,nVol),
            vonMisesFit[[iVox]][[2]][[iBlock]][[2]][[iVM]]))),stringsAsFactors=FALSE) ### all the variables become "factors", add "stringsAsFactors=FALSE"

       vonFitBlock <- rbind(vonFitBlock, IdvCurve)                 
    }
  
  vonFitCurve <- rbind(vonFitCurve,vonFitBlock)
}   


# modify the column names of each dataframe
colnames(vonFitCurve) <- c("Voxel", "Block", "SingleVolume", "FitVM", "value")

# transform some variables as numeric format
vonFitCurve$value <- as.numeric(vonFitCurve$value)
vonFitCurve$FitVM <- as.numeric(vonFitCurve$FitVM)
vonFitCurve$Voxel <- as.factor(vonFitCurve$Voxel)
vonFitCurve$Block <- as.factor(vonFitCurve$Block)



maxPeakVM_Block <- ddply(vonFitCurve, .(Voxel, Block, FitVM), summarise, 
                         maxValue = max(value),
                         minValue = min(value),
                         Value = ifelse(abs(maxValue)>abs(minValue),maxValue,minValue))

# avg maxPeak across all block
MaxPeakVM_avg <- ddply(maxPeakVM_Block, .(Voxel, FitVM), summarise,
                         nlength = length(unique(Block)),
                         avgValue = mean(Value),
                         stePeak = sd(Value)/sqrt(nlength))


# get maxPeak of each fitVM in each block
# maxPeakVM_Block <- ddply(vonFitCurve, .(Voxel, Block, FitVM), summarise, 
#                          maxValue = max(value))
# 
# # avg maxPeak across all block
# MaxPeakVM_avg <- ddply(maxPeakVM_Block, .(Voxel, FitVM), summarise,
#                          nlength = length(unique(Block)),
#                          avgValue = mean(maxValue),
#                          stdPeak = sd(maxValue)/sqrt(nlength))




# add name of Subj ROI, xyz, and orientation in the dataframe
Coord <- ddply(datToFit, .(Voxel), summarise,
               x = mean(x), y = mean(y), z = mean(z))

MaxPeakVM_avg$Orient <-seq(-pi/2, pi/2, length.out = length(unique(MaxPeakVM_avg$FitVM))) # add radious of seq to data 

# ## save data as csv

fitVM_BOLD <- merge(MaxPeakVM_avg, Coord, by="Voxel")  
fitVM_BOLD$Subj <- unique(datToFit$Subj)
fitVM_BOLD$ROIs <- unique(datToFit$ROIs)
fitVM_BOLD <- arrange(fitVM_BOLD, Voxel, FitVM)
write.csv(fitVM_BOLD, file = saveCSV1, row.names= FALSE)
write.csv(vonFitCurve, file = saveCSV2, row.names= FALSE)
save(vonMisesFit, file=savRDdata) # save list info

```


```{r plotVM}
## random select 10 voxels to plot
avgZSigCh$Voxel <- as.factor(avgZSigCh$Voxel)
avgZSigChSel <- droplevels(subset(avgZSigCh, ROIs=='rOFA')) 
avgZSigChSel2 <- droplevels(subset(avgZSigChSel, Voxel%in%sample(levels(Voxel),10))) # random select 10 voxels to plot
maxAmpVMSel <- MaxPeakVM_avg[MaxPeakVM_avg$Voxel %in% avgZSigChSel$Voxel, ] # get same voxels from avgZSigChSel
#maxAmpVMSel <- MaxPeakVM_avg
### plot original avg curve
dev.new()
ggplot(data=avgZSigChSel, aes(x=SingleVolume, y=avgSigSM)) +
  theme_few() + 
  facet_wrap(~Voxel) + 
  geom_line(color='red') +
  geom_hline(aes(yintercept=0)) +
  ylim(-1, 1) +
  geom_errorbar(aes(ymin=avgSigSM-steSigSM, ymax=avgSigSM+steSigSM), width=0.1) +
  ylab("signal change % (normalized)") 
  
### recover the signal from max amp of each VM fitting
dev.new()
ggplot(data=maxAmpVMSel, aes(x=FitVM, y=avgValue)) +
  theme_few() + 
  facet_wrap(~Voxel, scale='free') + 
  geom_errorbar(aes(ymin=avgValue-stdPeak, ymax=avgValue+stdPeak), width=0.1) +
  geom_line(color='green') +
  geom_point(stat='identity') +
  geom_hline(aes(yintercept=0)) +
  ylim(-1, 1) +
  #scale_x_continuous(breaks=c(-pi, -pi/2, -pi/4, 0, pi/4, pi/2, pi), labels=rad2deg(c(-pi, -pi/2, -pi/4, 0, pi/4, pi/2, pi))) +
  ylab("Max Amp from models") 

```

# check single trial fitting 
```{r plotSingleTrialVM}
### recover the signal from max amp of each VM fitting
 
datToFit$newZsigSM <- datToFit$zSigSM
datToFit$newZsigSM <- ifelse(datToFit$newZsigSM<0, 0, datToFit$newZsigSM) # treat negative signal as zero


dev.new()
ggplot(data=datToFit, aes(x=SingleVolume, y=zSigSM)) +
  theme_few() + 
  facet_wrap(Voxel~Block) + 
  geom_line(color='red') +
  geom_hline(aes(yintercept=0)) +
  #geom_errorbar(aes(ymin=avgSigSM-steSigSM, ymax=avgSigSM+steSigSM), width=0.1) +
  ylab("signal change % (normalized)") +
  ggtitle("original BOLD resp in each block")


### plot each fit curve in each block
vonFitCurve$Block <- as.numeric(vonFitCurve$Block)
dev.new()
ggplot(data=vonFitCurve, aes(x=as.numeric(SingleVolume), y=value, group=FitVM)) +
  theme_few() + 
  facet_wrap(Voxel~Block) + 
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("13 FitCurves in each block")
  

### plot avg fit curves in each block 
avgCurve <- ddply(vonFitCurve, .(Voxel, Block, SingleVolume), summarise,
                  avgFit = mean(value))
dev.new()
ggplot(data=avgCurve, aes(x=as.numeric(SingleVolume), y=avgFit)) +
  theme_few() + 
  facet_wrap(Voxel~Block) + 
  #geom_errorbar(aes(ymin=avgVM-steVM, ymax=avgVM+steVM), width=0.1) +
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("avg FitCurves in each block")


### plot avg curve across all block
avgCurveAll <- ddply(avgCurve, .(Voxel, SingleVolume), summarise,
                  avgVM = mean(avgFit))
dev.new()
ggplot(data=avgCurveAll, aes(x=as.numeric(SingleVolume), y=avgVM)) +
  theme_few() + 
  #facet_wrap(Voxel~Block) + 
  #geom_errorbar(aes(ymin=avgVM-steVM, ymax=avgVM+steVM), width=0.1) +
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("avg FitCurves across all blocks")


### plot max curve in each block
maxCurve <- ddply(vonFitCurve, .(Voxel, Block, SingleVolume), summarise,
                  maxVM = max(value))
dev.new()
ggplot(data=maxCurve, aes(x=as.numeric(SingleVolume), y=maxVM)) +
  theme_few() + 
  facet_wrap(Voxel~Block) + 
  #geom_errorbar(aes(ymin=avgVM-steVM, ymax=avgVM+steVM), width=0.1) +
  ylim(-2,2) +
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("max FitCurves in each block")


### get max of each VM in a block
MaxPeakCurve <- ddply(vonFitCurve, .(Voxel, Block, FitVM), summarise,
                  maxPeak = max(value))
dev.new()
ggplot(data=MaxPeakCurve, aes(x=as.numeric(FitVM), y=maxPeak)) +
  theme_few() + 
  facet_wrap(Voxel~Block) + 
  #geom_errorbar(aes(ymin=avgVM-steVM, ymax=avgVM+steVM), width=0.1) +
  #ylim(-2,2) +
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("max FitCurves in each block")

### avg MaxPeak across all block
avgMaxPeakCurve <- ddply(MaxPeakCurve, .(Voxel, FitVM), summarise,
                         nlength = length(unique(Block)),
                         avgmaxPeak=mean(maxPeak),
                         stdPeak = sd(maxPeak)/sqrt(nlength))

dev.new()
ggplot(data=avgMaxPeakCurve, aes(x=as.numeric(FitVM), y=avgmaxPeak)) +
  theme_few() + 
  facet_wrap(~Voxel) + 
  geom_errorbar(aes(ymin=avgmaxPeak-stdPeak, ymax=avgmaxPeak+stdPeak), width=0.1) +
  #ylim(-2,2) +
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("avg max FitCurves across blocks")




                         
### plot each fixed fitting results in 32 blocks
dev.new()
ggplot(data=vonFitCurve, aes(x=as.numeric(SingleVolume), y=value, group=Block)) +
  theme_few() + 
  facet_wrap(Voxel~FitVM) + 
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("Each Fixed fitting results in 32 blocks")


### plot max 13 curves across all blocks
dev.new()
ggplot(data=vonFitCurve_Avg, aes(x=as.numeric(SingleVolume), y=avgVM)) +
  theme_few() + 
  facet_wrap(Voxel~FitVM) + 
  geom_line(color='green') +
  geom_hline(aes(yintercept=0)) +
  ggtitle("avg Fixed fitting across all blocks")



```





*** 1_step to fit VM model ***
first, we fix the orientation tuning between [-2/pi 2/pi], like we can make 10 or 20 orientation tuning (need to check V1 or monkey studies), limit the range of base and amp, and then fit one VM function for many times (i.e. 1500), using randomly chosen inital seed values on each iteration (across the range of allowable values) to ensure the fitting algorithm did not settle in a local min. The set of parameters for each voxel that yielded the lowest root mean squared error across the i.e. 1500 iterations. In this case, we can remove negative signal to baseline (i.e. close to 0)   
```{r VModel_1stStep}
## Fitting the model to the data. The fit is done using nonlinear least squares
vonMises_1stFitData <- function(inputData) ## time series
  {
  
  allBlock <- list()
  allfit2Vox <- list()
  OrientFitPar <- list()
  kk=0
  for (ixVoxel in levels(droplevels(as.factor(inputData$Voxel)))) {
    kk=kk+1
    for (ixBlock in levels(droplevels(as.factor(inputData$Block)))){
      oneVoxelData <- subset(inputData, inputData$Voxel == ixVoxel & inputData$Block==ixBlock)
      
      Xtime <- oneVoxelData$SingleVolume
      cat("Trial=", kk, "of", length(unique(datToFit$Voxel)), "\n")
      print(paste("Voxel", ixVoxel))
      print(paste("Block", ixBlock))
    
     oneVoxelTS <- oneVoxelData$zSigSM # smooth or raw signal
      maxPeak <- round(max(oneVoxelTS))
      minPeak <- round(min(oneVoxelTS))
      mus <- seq(-pi/2,pi/2, length.out=13)
      
      for (ixOrient in mus){
        
        ixOrientSeq <- match(ixOrient, mus) # find index of mus for return VM data
        # print(paste("ixOrient", ixOrient))
        # random search range
        guessBase <- c(0)
        guessAmp <- c(-2,2) #seq(minPeak,maxPeak, by=0.005) #c(-3,3)
        
        guessKap <- 10*pi
        
        st1 <- data.frame(base = guessBase, amp = guessAmp, prefOr = ixOrient, kap = guessKap) 
        alg <- "plinear-random" #"plinear-random"
        maxIt <- 150 # for plinear-random
        
        resfit <- nls2(oneVoxelTS~Model_Pes(base,amp,prefOr, kap), 
                       start=st1, algorithm=alg,trace=FALSE,
                       control=nls.control(maxiter= maxIt, minFactor=1/1024,  warnOnly=TRUE)) 
        
        OrientFitPar[[ixOrientSeq]] <- predict(resfit)
        
        }
      allBlock[[ixBlock]] <- list("Block" = ixBlock, OrientFitPar)
      
      } # for ixBlock
    
    allfit2Vox[[ixVoxel]] <- list("Voxel" = ixVoxel, allBlock)
    
    } # for ixVoxel
  
  return(allfit2Vox)
  
  }
```


*** VonMises function ***
Using Pestilli's paper
```{r VMfun2Step1}
    Model_Pes <- function (base,amp,prefOr, kap)
      {
      #browser()
      orientations <- seq(-pi/2, pi/2, length.out = 9)
      #circularNormal <- base + dvm(orientations, prefOr1, kap1)
      circularNormal <- base + amp * exp(kap * (2*cos(orientations-prefOr) - 1))  ## Pestilli et al, 2009 paper.
      }    
```






